Arrows for Parallel Computations

### 2017-12-15 paper/content/utilityFunctions.tex
wip

These combinators make use of the |ArrowChoice| type class which provides the |pipepipepipe| combinator. It takes two arrows |arr a c| and |arr b c| and combines them into a new arrow |arr (Either a b) c| which pipes all |Left a|'s to the first arrow and all |Right b|'s to the second arrow:
% \begin{figure}[htb]
\begin{code}
(pipepipepipe) :: ArrowChoice arr a c -> arr b c -> arr (Either a b) c
\end{code}

@@

In Fig.~\ref{fig:profunctorArrow} we show how specific Profunctors can be turned into Arrows. Note that in Standard GHC |(>>>)| has the type |(>>>) :: Category cat => cat a b -> cat b c -> cat a c| and is therefore not part of the |Arrow| typeclass.

>>>>

These combinators make use of the |ArrowChoice| type class which provides the |pipepipepipe| combinator. It takes two Arrows |arr a c| and |arr b c| and combines them into a new Arrow |arr (Either a b) c| which pipes all |Left a|'s to the first arrow and all |Right b|'s to the second arrow:
% \begin{figure}[htb]
\begin{code}
(pipepipepipe) :: ArrowChoice arr a c -> arr b c -> arr (Either a b) c
\end{code}

@@

In Fig.~\ref{fig:profunctorArrow} we show how specific Profunctors can be turned into Arrows. This works because Arrows are strong Monads in the bicategory Prof of Profunctors as shown by \citet{Asada:2010:ASM:1863597.1863607}. Note that in Standard GHC |(>>>)| has the type |(>>>) :: Category cat => cat a b -> cat b c -> cat a c| and is therefore not part of the |Arrow| typeclass like presented in this paper.
